---
title: "r4d_HHSurvey_ModelSelection_LinearRegression"
author: "Biraj Adhikari"
date: "2023-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Model Selection
This file takes the imputed dataset as an input and runs model selection through multiple linear regression  
(with NCP Attitude Score as the response variable)

Requirements
```{r loading library}
library(dplyr)
```

#functions for this file:
```{r required functions}

fct_case_when <- function(...) {
  args <- as.list(match.call())
  levels <- sapply(args[-1], function(f) f[[3]])  # extract RHS of formula
  levels <- levels[!is.na(levels)]
  factor(dplyr::case_when(...), levels=levels)
}
```

# Data Import and Management

## Data Import
Since the results from imputation have response and explanatory variables separately, we need to combine this:
```{r data import and merge}
exp_vars <- readRDS("ImputationResults/clean_imputed_explanatory_dataset.rds")
exp_vars <- data.frame(exp_vars)
#remove auxillary variables:
explanatory_variables <- strsplit("Location, Caste, House.Material, Gender, Age, Farmpc, Occupation, Nature, Ladder, EnoughFood, EnoughIncome, LandPrice, tlu, Healthy, WaterShortage, EnergySuff, ElectricitySuff, Education, Drr", split = ", ")[[1]]
exp_vars <- exp_vars[, explanatory_variables]
rm(explanatory_variables)

exp_vars <- exp_vars %>% 
  mutate(ID = factor(seq(1, nrow(exp_vars)))) %>%
  relocate(ID, .before = "Location")

res_vars <- readRDS("ImputationResults/clean_imputed_response_dataset.rds")

res_vars <- res_vars %>% 
  mutate(ID = factor(seq(1, nrow(res_vars)))) %>%
  relocate(ID, .before = "NatureFood")

#merge explanatory and response variables by common ID
maindata <- merge(res_vars, exp_vars, by = "ID")

rm(exp_vars, res_vars)
```

## Data Management
```{r data cleaning}
#creating ncp_index variable
#first converting ncp perception variables to numeric
ncpsubset <- maindata %>%
  select(NatureFood, NatureWork, NatureHealth, NatureWater, 
         NatureEnergy, NatureEducation, NatureDrr, NatureRecrea, 
         NatureCulture) %>%
  sapply(as.numeric) %>%
  as.data.frame() %>%
  mutate(index = round(rowMeans(.), 3))

maindata <- maindata %>% 
  mutate(ncp_index = ncpsubset$index) %>%
  relocate(ncp_index, .before = "Location")

rm(ncpsubset)

#making necessary conversions
maindata <- maindata %>%
  
#EDUCATION
mutate(Education = fct_case_when(
  Education == "Uneducated" ~ "Illeterate", #I think this word makes more sense
  Education == "Basic Read/Write" ~ "Basic Literacy",
  Education == "Primary Education" ~ "Primary",
  TRUE ~ "Secondary or more"
)) %>%

#OCCUPATION
mutate(Occupation = fct_case_when(
  Occupation == "Agriculture" ~ "Agriculture",
  Occupation == "Daily Wage" ~ "Daily Wage",
  TRUE ~ "Employment & Business"
)) %>%
  
#INCOME SUFFICIENCY  
mutate(EnoughIncome = fct_case_when(
  (EnoughIncome == "Very sufficient") | (EnoughIncome == "Sufficient") ~ "Yes",
  TRUE ~ "No"
)) %>%
  
#HEALTH
mutate(Healthy = fct_case_when(
  (Healthy == "Very healthy") | (Healthy == "A bit healthy") ~ "Yes",
  TRUE ~ "No"
)) %>%

#WATER ACCESS
mutate(WaterAccess = fct_case_when(
    WaterShortage == 0 ~ "Yes",
    WaterShortage > 0 ~ "No"
  )) %>%

#ENERGY SUFFICIENCY
mutate(EnergySuff = fct_case_when(
  (EnergySuff == "Very sufficient") | (EnergySuff == "A bit sufficient") | (EnergySuff == "I don't know") ~ "Yes",
  TRUE ~ "No"
)) %>%
  
#ELECTRICITY SUFFICIENCY
mutate(ElectricitySuff = fct_case_when(
  (ElectricitySuff == "Very Sufficient") | (ElectricitySuff == "A bit sufficient") | (ElectricitySuff == "I don't know") ~ "Yes",
  TRUE ~ "No"
)) %>%

#DISASTER FREE OR NOT  
mutate(DisasterFree = fct_case_when(
  Drr == "No Incidences" ~ "Yes",
  TRUE ~ "No"
)) %>%



select(-WaterShortage, -Drr)
  
```

## Saving the data
```{r saving data for regression analysis}
saveRDS(maindata, "hh_data_for_regression_March2023.RDS")
```

# Chronbach's Alpha Test
```{r chronbach's alpha}
library(ltm)

#dplyr's select will be masked from now on.
maindata %>% dplyr::select(NatureFood, NatureWork, NatureHealth, NatureWater, NatureEnergy, NatureEducation, NatureDrr, NatureRecrea, NatureCulture) %>% cronbach.alpha(na.rm = TRUE, CI = TRUE, standardized = TRUE)
```
  
Chronbach's Alpha = 0.796, which is good.    

# Correlation Check  
Note: In most cases, a correlation coefficient of 0.7 or higher for two variables means that we should probably exclude one of them in the analysis. However, I haven't found a really nice reference for this.
```{r correlation plots}
#selecting only explanatory variables
library(polycor)
library(corrplot)

testdata <- maindata %>%
 dplyr::select(Location, Caste, Gender, Age, Farmpc,
         Occupation, Nature, Ladder, EnoughFood, EnoughIncome,
         LandPrice, Healthy, EnergySuff, ElectricitySuff, Education,
         WaterAccess, DisasterFree, tlu)
 
maindata_cor <- hetcor(testdata, use = "pairwise.complete.obs")
rm(testdata)
#plotting
corrplot(maindata_cor$correlations, method = "circle", type = "lower", 
         tl.col = "black", tl.srt = 45, diag = F, order = "hclust", addCoef.col = "black", number.cex = 0.6)
rm(maindata_cor)
```

Correlation between Location and Caste is high. Giving a closer look:    
```{r Location and Caste Correlation}
#Location and Caste
table(maindata[, c("Location", "Caste")])
mosaicplot(table(maindata[, c("Location", "Caste")]), main = "Mosaic plot", color = TRUE)
```  

We see that Location and Caste variables couldn't totally be seperated.   
Yamphudin is predominantly of "Ethnic" caste, i.e. people who do not confirm to the caste system.  
Sulubung is mixed, while Bahundangi has predominantly higher castes.  
**Decision:** Remove Caste and retain Location into the main model.

# Removal of one outlier  
Note: This was identified with multiple rounds during the model selection process.
```{r outlier removal}
maindata = maindata %>% filter(LandPrice < max(maindata$LandPrice))
#There is only one LandPrice which seems abnormally high (might be because of some kind of mistake, but this data point seems to be an influencial outlier. So, we removed it)  
```

# Model Selection
Essential Variables::  
**Location: ** With the hypothesis that location matters on people's perception towards nature. This is important to measure so that conservation activities take into consideration the needs and priorities of local communities.  

**Education: ** Since based on my second chapter, Education is one of the goal that really can synergize with conservation goals. Also, preexisting studies show strong relationships between people's percetption towards conservation activities and thier education level.  

**Wellbeing Variables: ** These are accessibility variables: EnoughFood, EnoughIncome, EnergySuff, WaterAccess, Healthy, DisasterFree. Basically, we need to know what is the relationship between people's perceived wellbeing and perceived contribution of nature to thier wellbeing. Our hypothesis is that people with high levels of wellbeing are more positive towards nature. This result could strengthen the need for conservation policies that are people-focussed.  

## Non-Essential Variables::  
Remaining variables that will be selected through dredge.  
This also includes interaction terms between Location and the remaining "essential variables".


## Complete Model:  
```{r model selection first iteration}
complete_model = lm(ncp_index ~ Location + Age + Education +
                 LandPrice + Education + Gender + tlu + 
                 EnoughFood + Farmpc + EnoughIncome + Healthy + 
                 WaterAccess + EnergySuff + ElectricitySuff + DisasterFree + 
                 Ladder + Occupation + Nature + 
                   
                   #intearction terms::
                   
                  Location*Caste + Location*Education +
                 Location*EnoughFood + Location*EnoughIncome +
                  Location*Healthy + Location*WaterAccess +
                  Location*EnergySuff + Location*DisasterFree, data = maindata)
```

## Dreging:
The "essential variables will be kept in the final model no matter what. We then calculate each and every combination of these essential variables with the remaining variables plus interaction terms, and calculated the AICc for each.  

```{r dredging, eval=FALSE, echo=FALSE}
#defining the fixed (or essential) variables:
fixed_variables = c("Location", "EnoughFood", "EnoughIncome", 
                    "Healthy", "WaterAccess", "EnergySuff", 
                    "DisasterFree", "Education")
#dredging
#note: this is not calculated since it takes a lot of time.
#instead, i have saved the first 20 models of the dredge function
options(na.action = "na.fail") # Required for dredge to run
model_selection <- dredge(model_complete, beta = "none", fixed = fixed_variables)
options(na.action = "na.omit") # set back to default
```  

Note: The model_selection is stored locally because the size it very large. Only a subset of top 20 models have been uploaded into the GitHub repository:

```{r reading top 20 models from dredge}
model_selection_subset <- readRDS("model_selection_subset20.RDS")
#visualizing AIC Values
plot(model_selection_subset$AICc)
abline(h = (min(model_selection_subset$AICc) + 2), col = "red")
```  

There are 5 models with delAICc <=2. Looking at these models closely:
```{r 5 top models AICc}
head(model_selection_subset, 5)
```
```{r checking the vifs for each model}
#Checking VIFs 
library(car)
library(MuMIn)
vif(get.models(model_selection_subset, subset = 1)[[1]])
vif(get.models(model_selection_subset, subset = 2)[[1]])
vif(get.models(model_selection_subset, subset = 3)[[1]])
vif(get.models(model_selection_subset, subset = 4)[[1]])
vif(get.models(model_selection_subset, subset = 5)[[1]])
```

All VIF values are okay. 
We then proceed to select the most parsimonious model, which is the 2nd model.  

# Linear Regression using the selected model
```{r getting the final selected model}
#note, we could use the get.models function but I think it makes more sense to explicitly define them
model <-lm(ncp_index ~ Location + Gender + Ladder + Farmpc +
             EnoughFood + EnoughIncome + Healthy + WaterAccess +
             EnergySuff + Education + DisasterFree + 
             Location * Healthy + Location * WaterAccess, data = maindata)

summary(model)
```  

Two Interaction Terms: Location|Healthy and Location|WaterAccess have been retained in the model. Plotting the interactions:
```{r plotting interaction terms}
library(lattice)
interaction.plot(x.factor = maindata$Location, trace.factor = maindata$Healthy, response = maindata$ncp_index)
interaction.plot(x.factor = maindata$Location, trace.factor = maindata$WaterAccess, response = maindata$ncp_index)
```  
Indeed, the interaction effect looks significant.
```{r extracting coeff table 24Apr 23}
model.coef <- round(summary(model)$coef, 3)
signf <- ifelse(model.coef[,4] < 0.05, 1, 0)
model.coef.extract <- cbind(model.coef, signf)

write.csv(model.coef.extract, file = "RegressionResults/LinearRegResults_May2023.csv")
#23May Note: Check whether the format of the file is okay.
```  

### Diagnostic Plots  
Based on the figures below, model diagnostics looks good.  
```{r diagnostic plots}
par(mfrow = c(2,2))
plot(model)
```


## Sensitivity Analysis  
### Caste-Location Interchange  
```{r caste location sensitivity analysis}
modelcaste <-lm(ncp_index ~ Caste + Gender + Ladder + Farmpc +
             EnoughFood + EnoughIncome + Healthy + WaterAccess +
             EnergySuff + Education + DisasterFree + 
             Caste * Healthy + Caste * WaterAccess, data = maindata)

summary(modelcaste)

#as before, extracting the caste variables::
model.coef <- round(summary(modelcaste)$coef, 3)
signf <- ifelse(model.coef[,4] < 0.05, 1, 0)
model.coef.extract <- cbind(model.coef, signf)

write.csv(model.coef.extract, file = "SensitivityResults/Sensitivity_Caste.xlsx")
```

### Sensitivity Analysis (other top-5 models)  
A synthesis of sensitivity analysis for the remaining 4 models is available in the Supplementary Materials.
```{r sensitivity analysis top-5 models}
#We take the third model for the main analysis. There are 4 other models with del.AIC <=2. We calculate the coefficients table for each of these models

library(MuMIn)
#Model 1
senmodel1 <- (get.models(model_selection_subset, subset = 1)[[1]])

model.coef <- round(summary(senmodel1)$coef, 3)
signf <- ifelse(model.coef[,4] < 0.05, 1, 0)
model.coef.extract <- cbind(model.coef, signf)

write.csv(model.coef.extract, file = "SensitivityResults/Sensitivity_delAICModel1.csv")

#Model 2
senmodel2 <- (get.models(model_selection_subset, subset = 2)[[1]])

model.coef <- round(summary(senmodel2)$coef, 3)
signf <- ifelse(model.coef[,4] < 0.05, 1, 0)
model.coef.extract <- cbind(model.coef, signf)

write.csv(model.coef.extract, file = "SensitivityResults/Sensitivity_delAICModel2.csv")

#we used model 3 as the main model
#Model 4
senmodel4 <- (get.models(model_selection_subset, subset = 4)[[1]])

model.coef <- round(summary(senmodel4)$coef, 3)
signf <- ifelse(model.coef[,4] < 0.05, 1, 0)
model.coef.extract <- cbind(model.coef, signf)

write.csv(model.coef.extract, file = "SensitivityResults/Sensitivity_delAICModel4.csv")

#Model 5
senmodel5 <- (get.models(model_selection_subset, subset = 5)[[1]])

model.coef <- round(summary(senmodel5)$coef, 3)
signf <- ifelse(model.coef[,4] < 0.05, 1, 0)
model.coef.extract <- cbind(model.coef, signf)

write.csv(model.coef.extract, file = "SensitivityResults/Sensitivity_delAICModel5.csv")

rm(senmodel1, senmodel2, senmodel4, senmodel5)
```



