---
title: "r4d_HHSurvey_DataCleaning"
author: "Biraj Adhikari"
date: "2023-05-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r requirements}
library(dplyr)
#Functions I use
#function to directly convert numbers into categorical variables
fct_case_when <- function(...) {
  args <- as.list(match.call())
  levels <- sapply(args[-1], function(f) f[[3]])  # extract RHS of formula
  levels <- levels[!is.na(levels)]
  factor(dplyr::case_when(...), levels=levels)
}

#This is for Trends in Ecosystems
forLikert <- function(trend) {
  trend = fct_case_when(
    trend ==1 ~ "Increased a lot",
    trend ==2 ~ "Increased a bit",
    trend ==3 ~ "No Change/I don't know",
    trend ==4 ~ "Decreased a bit",
    trend ==5 ~ "Decreased a lot"

  )
}

#This is for developmental trends
forLik_Dev <- function(trend) {
  trend = fct_case_when(
    trend ==1 ~ "Improved a lot",
    trend ==2 ~ "Improved a bit",
    trend ==3 ~ "No Change/I don't know",
    trend ==4 ~ "Worsened a bit",
    trend ==5 ~ "Worsened a lot"
  )
}
```

## Data Reading  
```{r reading data for imputation}
hh <- read.csv("r4d_RawData_HouseholdNepal.csv", sep = ",", header = TRUE)

#first, i will remove some problematic variables that should not be considered at all
hh = hh %>% select(-c("Ward.Village.name", "q7_AgroWildlife", "q19A_GrasslandEcosystem", "q26_Huntpc",
                      "q41_HealthTrends","q44_Toilet", "q51_Cook",
                      "q59_FamEducation", "q70_Recre", "q75_Culture"))
```  

These variables are removed for the following reasons:  

Ward/Village name is only for information for stakeholders  
q7_AgroWildlife because enumerators had confusion about this and ended up asking different things  
q19A_GrasslandEcosystem because we didn't ask this question in one location entirely  
q26_Huntpc because only people from one location said they hunted for food. Additionally, enumerators said people were not honest about this answer  
q41_HealthTrends: While the purpose of this was to see if in general, the status of health of household was improving or not, the participants felt we were talking about their own health (so, older people perceived their health was deteriorating over the years). We should have framed this question better...but for now, I think it is best that this is removed.  
q44_Toilet because almost every house we surveyed had toilets  
lot of confusion around q59_FamEducation by enumerators. So deleted  
q51_Cook: major households reported Firewood, except in Bahundangi, who reported gas. I think this variable is best removed from the analysis  
q70_Recre and q75_Culture are not relevant for the analysis  

## Data Cleaning  
Conversion of numerical variables into factors:  
```{r data cleaning 1}
hh = hh %>% 
  #TYPE OF HOUSE
  mutate(
    House.Material = fct_case_when( 
      House.Material == 1 ~ "Cement/Bricks/Concrete/Wood",
      House.Material == 2 ~ "Mud/Thached/Straws"
      # TRUE ~ as.character(House.Material)
    )
  ) %>%
  
  #GENDER
  mutate(
    Gender = fct_case_when(
      Gender == 1 ~ "Female",
      Gender == 2 ~ "Male"
      #  TRUE ~ as.character(Gender)
    )
  ) %>%
  
  #EDUCATION
  mutate(
    Education = fct_case_when(
      Education == 5 ~ "Bachelors' Completed or more",
      Education == 4 ~ "Secondary Education",
      Education == 3 ~ "Primary Education",
      Education == 2 ~ "Basic Read/Write",
      Education == 1 ~ "Uneducated"
      
      #    TRUE ~ as.character(Education)
    )
  ) %>%
  
  #ENOUGH FOOD
  mutate(
    q24_EnoughFood = fct_case_when(
      q24_EnoughFood == 1 ~ "Yes",
      q24_EnoughFood == 0 ~ "No"
      
      
      #  TRUE ~ as.character(q24_EnoughFood)
    )
  ) %>%
  
  #ENOUGH INCOME
  mutate(
    q30_EnoughIncome = fct_case_when(
      q30_EnoughIncome == 1 ~ "Very sufficient",
      q30_EnoughIncome == 2 ~ "Sufficient",
      q30_EnoughIncome == 3 ~ "I don't know",
      q30_EnoughIncome == 4 ~ "Insufficient",
      q30_EnoughIncome == 5 ~ "Very insufficient"
      
      #  TRUE ~ as.character(q30_EnoughIncome)
    )
  ) %>%
  
  #HEALTHY (note, in the analysis, we convert healthy into categorical variable of 2 levels)
  mutate(
    q35_Healthy = fct_case_when(
      q35_Healthy == 1 ~ "Very healthy",
      q35_Healthy == 2 ~ "A bit healthy",
      q35_Healthy == 3 ~ "A bit unhealthy",
      q35_Healthy == 4 ~ "Very unhealthy"
      
      #   TRUE ~ as.character(q35_Healthy)
    )
  ) %>%
  
  #ELECTRICITY
  mutate(
    q50_Electricity = fct_case_when(
      q50_Electricity == 1 ~ "Yes",
      q50_Electricity == 0 ~ "No"
      
      
      #   TRUE ~ as.character(q50_Electricity)
    )
  ) %>%
  
  #ENERGY SUFFICIENCY (note that we use only 2 factors in the analysis)
  mutate(
    q54_EnergySuff = fct_case_when(
      q54_EnergySuff ==1 ~ "Very sufficient",
      q54_EnergySuff ==2 ~ "A bit sufficient",
      q54_EnergySuff ==3 ~ "I don't know",
      q54_EnergySuff ==4 ~ "A bit insufficient",
      q54_EnergySuff ==5 ~ "Very insufficient"
      
      #   TRUE ~ as.character(q54_EnergySuff)
    )
  ) %>% 
  
  mutate(
    q55_ElectricitySuff = fct_case_when(
      q55_ElectricitySuff ==1 ~ "Very Sufficient",
      q55_ElectricitySuff ==2 ~ "A bit sufficient",
      q55_ElectricitySuff ==3 ~ "I don't know",
      q55_ElectricitySuff ==4 ~ "A bit insufficient",
      q55_ElectricitySuff ==5 ~ "Very insufficient"
      
      #     TRUE ~ as.character(q55_ElectricitySuff)
    )
  ) %>% 
  
  
  #DRR
  mutate(
    q64_Drr = fct_case_when(
      q64_Drr == 4 ~ "No Incidences",
      q64_Drr == 3 ~ "A few minor incidences",
      q64_Drr == 2 ~ "Many minor incidences",
      q64_Drr == 1 ~ "One or more major incidences"
    )
  ) %>%
  
  #DRR Trends Reversed (since increase in DRR means a negative trend unlike the other variables)
  #i did this to undo the mistake of reversing the sign here
  mutate(
    q66_DrrTrends = case_when(
      q66_DrrTrends == 1 ~ 5,
      q66_DrrTrends == 2 ~ 4,
      q66_DrrTrends == 3 ~ 3,
      q66_DrrTrends == 4 ~ 2,
      q66_DrrTrends == 5 ~ 1
    )
  ) %>%
  
  #ConservationNature
  mutate(q82_ConservationNature = fct_case_when(
    q82_ConservationNature == 1 ~ "Benefits a lot",
    q82_ConservationNature == 2 ~ "Benefits a bit",
    q82_ConservationNature == 3 ~ "No effect/I don't know",
    q82_ConservationNature == 4 ~ "Harms a bit",
    q82_ConservationNature == 5 ~ "Harms a lot"
  )) %>%
  
  mutate(q84_ConservationPeople = fct_case_when(
    q84_ConservationPeople == 1 ~ "Benefits a lot",
    q84_ConservationPeople == 2 ~ "Benefits a bit",
    q84_ConservationPeople == 3 ~ "No effect/I don't know",
    q84_ConservationPeople == 4 ~ "Harms a bit",
    q84_ConservationPeople == 5 ~ "Harms a lot"
  ))
```  

Converting dummy variables from numeric to categorical::

```{r data cleaning 2}
dummyvars = c("q37_HealthCheck_Hospital", "q37_HealthCheck_Aayurved", "q37_HealthCheck_Homemade", "q37_HealthCheck_Pharmacy",
              "q37_HealthCheck_Dhami", "q43_WaterSource_Tap", "q43_WaterSource_River", "q43_WaterSource_Tube", "q43_WaterSource_Spring",
              "q43_WaterSource_Well", "q43_WaterSource_Lake","q43_WaterSource_Others", "q60_EnvEducation_School",
              "q60_EnvEducation_Media", "q60_EnvEducation_Fam" ,"q60_EnvEducation_Elders", "q60_EnvEducation_NGO",
              "q60_EnvEducation_Others")

hh[,dummyvars] = lapply(hh[,dummyvars], as.factor)
rm(dummyvars)
```  

```{r data cleaning 3}
#converting nature-trend variables from numeric to factor
trendvars = c("q5_AgriTrends", "q6_AgroDiversity", "q11_ForestArea", "q12_ForestQuality", 
              "q13_ForestWildlife", "q15_FreshwaterQuant", "q16_FreshwaterQual",
              "q17_FreshwaterWildlife")

hh[,trendvars] = lapply(hh[, trendvars], forLikert)

#converting development-trend variables from numeric to factor (i replace the same trendvars variable here)
trendvars = c("q22_FoodTrends", "q33_IncomeTrends", "q48_WaterTrends", 
              "q56_EnergyTrends", "q57_ElectricityTrends", "q62_EducationTrends", "q66_DrrTrends")

hh[,trendvars] = lapply(hh[, trendvars], forLik_Dev)

rm(trendvars)
#Occupation variable needs a bit of adjustment
hh = hh %>% 
  mutate(
    Occupation = fct_case_when(
      q29_Occupation_Agriculture == 1 ~ "Agriculture",
      q29_Occupation_Business == 1 | q29_Occupation_Tourism == 1 ~ "Business",
      
      q29_Occupation_Health == 1 | q29_Occupation_Government == 1  | q29_Occupation_Education == 1 | q29_Occupation_Private == 1 ~ "Employment",
      
      q29_Occupation_Others == 1 ~ "Foreign Employment",
      q29_Occupation_Labour == 1 ~ "Daily Wage"
      
    ))

hh = hh %>% select(-c("q29_Occupation_Agriculture", "q29_Occupation_Business",
                      "q29_Occupation_Tourism", "q29_Occupation_Health",
                      "q29_Occupation_Government", "q29_Occupation_Education",
                      "q29_Occupation_Private", "q29_Occupation_Others", 
                      "q29_Occupation_Labour"))
```  

Making the levels of categorical variables intuitive and consistent::  
```{r data cleaning 4}
#all other categorical variables (Although most variables are repeated, the levels are in different order
#so this helps put levels in consistent order)
hh$Location = factor(hh$Location, levels = c("Bahundangi", "Sulubung", "Yamphudin"))
hh$Caste = factor(hh$Caste, levels = c("Ethnic", "Higher", "Lower"))
hh$Occupation = factor(hh$Occupation, levels  = c("Agriculture", "Daily Wage", "Employment",
                                                              "Foreign Employment", "Business"))
#wellbeing variables
hh$q24_EnoughFood = factor(hh$q24_EnoughFood, levels = c("Yes", "No"))

#nature perception  and WellbeingCluster categorical variable
hh$Nature = factor(hh$Nature, levels = c("Non-Living", "Living", 
                                         "Living and Non-living", "Spiritual and Abstract", "I don't know"))

#converting all NCP questions (response variables) to ordinal variables
hh$q20_NatureFood = factor(hh$q20_NatureFood, levels = c(1,2,3,4,5), ordered = TRUE)
hh$q31_NatureWork = factor(hh$q31_NatureWork, levels = c(1,2,3,4,5), ordered = TRUE)
hh$q39_NatureHealth = factor(hh$q39_NatureHealth, levels = c(1,2,3,4,5), ordered = TRUE)
hh$q45_NatureWater = factor(hh$q45_NatureWater, levels = c(1,2,3,4,5),ordered = TRUE)
hh$q52_NatureEnergy = factor(hh$q52_NatureEnergy, levels = c(1,2,3,4,5), ordered = TRUE)
hh$q61_NatureEducation = factor(hh$q61_NatureEducation, levels = c(1,2,3,4,5), ordered = TRUE)
hh$q67_NatureDrr = factor(hh$q67_NatureDrr, levels = c(1,2,3,4,5), ordered = TRUE)
hh$q74_NatureRecrea = factor(hh$q74_NatureRecrea, levels = c(1,2,3,4,5), ordered = TRUE)
hh$q79_NatureCulture = factor(hh$q79_NatureCulture, levels = c(1,2,3,4,5), ordered = TRUE)
```  
 
For land category, we can probably multiply the land price per ha with land size to get an estimate of price of land owned  
I found a website of the government that shows the price of land.  
#https://www.dolma.gov.np/office/dept/content/fiscal-year-2079-080-1659243606  
Since price also varies in one village based on things like whether it is close to river or not, etc, i used the average. The mountain region does not have this information. So i used values from another mountain district similar to the one from our site (Prangbung Village - For Yamphudin).  

```{r land price}
#adding a column that multiples the price of land per location with the area
hh = hh %>% mutate(LandPrice = case_when(
  Location == "Bahundangi" ~ 250000 * q27_Land_ha, #price of land per hectare in Bahundangi
  Location == "Sulubung" ~ 200000 * q27_Land_ha, #price of land per hectare in Sulubung
  Location == "Yamphudin" ~ 30000 * q27_Land_ha #price of land per hectare in Yamphudin
  ))

#removed the land_ha variable
hh = subset(hh, select = -q27_Land_ha)
```  

Column names are weird. This code changes columns to simpler names:  
```{r column name simple}
library(stringr) #for str_replace
hh_q = hh %>% select(matches("^q\\d+_.+"))
hh_q = hh_q %>% rename_all(~str_replace(.,"^q\\d+_","" ))
hh_non_q = hh %>% select(-matches("^q\\d+_.+"))
hh_modified = bind_cols(hh_non_q, hh_q)

rm(hh_q, hh_non_q, hh)

#ordering the variables so that it is easier:
hh_ordered = hh_modified %>% select(
  #non-wellbeing and demographic variables
  Location, Caste, House.Material, Gender, Age,  Farmpc, Occupation, Nature,
  
  #Response variables
  NatureFood, NatureWork, NatureHealth, NatureWater, NatureEnergy, 
  NatureEducation, NatureDrr, NatureRecrea, NatureCulture,
  
  #wellbeing variables
  Ladder, EnoughFood, EnoughIncome, LandPrice, tlu,
  Healthy, WaterShortage, EnergySuff, ElectricitySuff, Education, Drr,
  
  #Aux Variables
  #EcosystemTrends
  AgriTrends, AgroDiversity, ForestArea, ForestQuality, ForestWildlife,
  FreshwaterQual, FreshwaterQuant, FreshwaterWildlife,
  
  #Wellbeing Trends
  FoodTrends, IncomeTrends, WaterTrends, EnergyTrends, Electricity, ElectricityTrends,
  EducationTrends, DrrTrends,
  
  #Multiple choice (dummy) variables
  HealthCheck_Hospital, HealthCheck_Aayurved, HealthCheck_Homemade, HealthCheck_Pharmacy,
  HealthCheck_Dhami, WaterSource_Tap, WaterSource_River, WaterSource_Tube, WaterSource_Lake,
  WaterSource_Spring, WaterSource_Well, WaterSource_Others, EnvEducation_School, EnvEducation_Media,
  EnvEducation_Fam, EnvEducation_Elders, EnvEducation_NGO, EnvEducation_Others, 
  
  #conservation nature and people
  ConservationNature, ConservationPeople
)
```

Saving the final, cleaned dataset in file  
```{r saving cleaned file}
saveRDS(hh_ordered, file = "r4d_CleanData_HouseholdNepal.rds")
rm(hh_modified, hh_ordered)
```

